### 2013-11-30 paper/main.tex
more work on the engine model
Still trying to sort out the engine model so it can
be used with a controller.

% TODO - delta to steady state

Typical control systems have an associated time step which can be
varied and is crucial in determining the performance of
the controller with regard to the Nyquist frequency.
This model has no such constraint because one calculation step
corresponds directly to one engine ignition event.
The controller is effectively running at the same ``clock speed'' as
the engine.

@@

%\begin{figure}[!htbp]
%\begin{center}
%\includegraphics[scale=0.5]{img/schematic-no_control-ed1}
%\end{center}
%\caption{Linear engine model with an open loop controller.
%Inputs go through the simple controller to provide steps to the
%engine model.
%The output rpm, since it is in steps ($\Delta N$), is accumulated.}
%\label{fig:openloop}
%\end{figure}

%\begin{figure}
%\begin{center}
%\includegraphics[scale=0.8]{img/linear_engine_model_no_control_plot}
%\end{center}
%%\caption{Output of linear engine controller with a transient torque
%input and a fixed input duty cycle.  Matlab source given in
%Appendix \ref{app:olplot}}
%\label{fig:olplot}
%\end{figure}

>>>>

Typical control systems have an associated time step.
And the choice of this time step is crucial in determining performance
with regard to the Nyquist frequency.
However this model does not suffer from this issue because it is
inherently discrete.
A single ignition event of the engine corresponds to a single
step of the model.

% TODO - reduced steady state system

Typical control system models have a single input and a single output
\footnote{One input/output could also be a vector.}.
However this model is different in that it takes
two inputs: control and torque (Figure \ref{fig:lem}).
One way to reduce the model to a single input single output is to hold
one of the inputs constant.
However neither of the resulting use cases would make any sense to
a designer whose primary goal is to stabilize engine rpm.
The first case, with torque constant, would indicate the response for
control inputs.
But this is pointless because the goal of idle stabilization is to
regulate the rpm given changes in torque.
The second case, with control held constant, would indicate the response
for a change in torque.
But again this would provide no useful way to stabilize engine rpm.
Both inputs are needed in order to construct any viable control system.

\section{Regulator Control System}

What is needed is a regulator system where the input is applied
as torque.
The general system is shown in Figure \ref{fig:rpm1}.

% {{{ engine regulator system
\begin{figure}[hbp!]
\begin{center}

	\node[gain] 	(engine)	[]					{engine};
	\node[gain] 	(control)	[below=of engine]	{controller};

	\draw [<-] (engine.north) -- ++(0,10mm) node[above]{$\text{torque}$};
	\draw [->] (engine.east) node[above,xshift=7mm]{rpm}
					-- ++(20mm,0)
					|- (control.east);
	\draw [->] (control.west)
					-- ++(-20mm,0)
					|- (engine.west) node[above,xshift=-9mm]{control};
\end{tikzpicture}

\end{center}
\caption{General system for regulating engine rpm.}\label{fig:rpm1}
\end{figure}
% }}}

@@
